`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-02-03 inst/manuscript/manuscript.rmd
Amend funding statement as requested by editorial staff;
Include 'Additional Files' section and approrpiate referencing, as requested by editorial staff;

The package is available as an `R` source package in the version current at
acceptance for publication in the supplementary material and may be installed
from that file using `install.packages(file.choose(), type = 'source')`.

@@

## Funding {-}
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21.

@@

>>>>

The package is available as an `R` source package in the version current at
acceptance for publication as Additional file 1 and may be installed
from that file using `install.packages(file.choose(), type = 'source')`.

@@

## Funding {-}
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21. No funding body was involved in the design of or conclusions drawn
from this study.

@@

# Additional Files {-}
Additional file 1: `R` source package of `flippant` in the version current at
acceptance for publication.
